% LaTeX resume using res.cls
\documentclass[margin]{res}
%\documentclass[12pt]{article}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\usepackage{bibentry}
\nobibliography{DerekWeitzelResume}

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\huge\bf Derek J. Weitzel}

% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:

\moveleft.5\hoffset\centerline{Holland Computing Center}
 
% \moveleft.5\hoffset\centerline{Lincoln, NE 68522}
%\moveleft.5\hoffset\centerline{(402) 450-9237}
 \moveleft.5\hoffset\centerline{118 Schorr Center}
  \moveleft.5\hoffset\centerline{Lincoln, NE 68588}
\moveleft.5\hoffset\centerline{dweitzel@cse.unl.edu}
\moveleft.5\hoffset\centerline{\sl Last Updated: 9/22/2011}

\begin{resume}



 
\section{RESEARCH EXPERIENCE}
                {\sl Graduate Research Assistant} \hfill       May 2009 - Present \\
                University of Nebraska Ð Lincoln Holland Computing Center, Lincoln, NE
                \begin{itemize} \itemsep -2pt
                \item Designed distributed workflows to run scientific applications on the Open Science Grid.
                \item Developed data analysis tools using Hadoop MapReduce
                \item Created cross platform cluster visualization tools using C++ and OpenGL\\
                (http://www.youtube.com/djw8605)
                \item Open Science Grid Fellow August 2010 - May 2011
                 \item Gave HCC Tours, roughly 2 per month -- 2008 - 2011
                \end{itemize}
                
                

               


%\section{EXPERIENCE}

              {\sl Summer Graduate Researcher} \hfill        May 2010 - August 2010 \&\\
                Fermi National Accelerator Laboratory \hfill   May 2011 - August 2011
                  \begin{itemize}  \itemsep -2pt
                  \item Designed distributed computing and data workflows using Condor, a high throughput batch scheduler
                   \item Wrote and maintained user documentation for the Open Science Grid
                   \item Packaged and documented grid software for end users
                   \item Lead a group writing RPMs and using Fedora packaging software for OSG Software
                   \item Write Database Data Mining functions for the OSG and Teragrid (XSEDE) accounting Databases.
                   \item Research the submission of scientific workflows to private research clouds. 
                   \end{itemize} 

              {\sl Assistant System Administrator} \hfill May 2006 - May 2009 \\
                University of Nebraska -- Lincoln Holland Computing Center, 
                Lincoln, NE
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Assisted in super computer cluster administration of a top 500 system
                \item   Developed visual cluster monitoring software \\
                           (http://sourceforge.net/projects/fish-monitoring) 
                \end{itemize}
 
              
 
 
 
                {\sl Development Engineer Intern} \hfill            May 2008 - August 2008 \\
                International Business Machines (IBM), Austin, TX 
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Lead developer redesigning dynamic functional simulator using Python and C.
               
                 \end{itemize} 
      
      
      	    
                 
%                {\sl CADD Technician} \hfill        Summer 2005 \\
%                Specialized Engineering Solutions, Omaha, NE
%                  \begin{itemize}  \itemsep -2pt
%                   \item Drafted commercial, mechanical, and electrical systems.
%                   \item Assisted in specifying equipment for clients 
%                   \end{itemize} 
                   
\section{EDUCATION} 
        {\sl Masters of Science} Computer Science \\
                Specialization in Computer Engineering \\
                University of Nebraska -- Lincoln \\
                Graduation Date: May 2011 \\
                GPA: 3.9

                 {\sl Bachelor of Science} Computer Engineering \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                University of Nebraska -- Lincoln \\
                GPA: 3.5 \\ 
                \\
                

 


\newpage
\section{AWARDS}
\begin{itemize}
\item Outstanding Undergraduate Award, May 2009
\item OSG CS Fellowship 2010 - 2011
\item Best Poster at The Great Plains Network Annual Meeting: {\sl Hadoop at the University of Nebraska -- Lincoln }.  May 2009
 \item Best Presentation at: The Great Plains Network Annual Meeting: \textit{Campus Grids -- Bridging Campuses}.  May 2009
\end{itemize}

\section{PAPERS}
\begin{itemize}
\item \textbf{Weitzel, Derek}, Brian Bockelman, Dan Fraser, Ruth Pordes, and David Swanson. "Enabling Campus Grids with Open Science Grid Technology," \textit{Proceedings: Computing in High Energy Physics (2010)}
\item W Andrews, B Bockelman, D Bradley, J Dost, D Evans, I Fisk, J Frey, B Holzman, M Livny, T Martin, A McCrea, A Melo, S Metson, H Pi, I Sfiligoi, P Sheldon, T Tannenbaum, A Tiradani, F W\"{u}rthwein and \textbf{D Weitzel}. ``Early experience on using glideinWMS in the cloud,'' \textit{Proceedings: Computing in High Energy Physics (2010)}
\end{itemize}

\section{PRESENTATIONS}
\begin{itemize}
 \item \textbf{Derek Weitzel} and Brian Bockelman ``Running persistent jobs in {Condor},'' \textit{Presentation at Condor Week},  University of Wisconsin -- Madison.  May 2010
   \item ``Building Campus {HTC} Sharing Infrastructures,'' \textit{Presentation at Condor Week}, University of Wisconsin -- Madison.  May 2011  
\end{itemize}

\section{INVITED \\ PRESENTATIONS}
\begin{itemize}
\item ``Distributed AutoDock with the Open Science Grid (OSG) Match Maker,'' \textit{Presentation at the OSG All Hands Meeting}, Fermi National Accelerator Laboratory.  March 2010
\item ``Distributed XRootd,'' \textit{Presentation at the OSG Site Administration Meeting}, Vanderbilt University.  August 2010
\item ``Campus Grid Technology,'' \textit{Presentation at the OSG All Hands Meeting}, Harvard Medical School.  March 2011
 \item \textbf{Derek Weitzel}, Ruth Pordes, Miron Livny ``Open Science Grid,'' \textit{Poster at Scientific Discovery through Advanced Computing Conference}, Denver, CO.  July 2011
\item ``Installation of OSG User Production Services,'' \textit{Presentation at the OSG Summer Workshop}, Texas Tech University.  August 2011
\end{itemize}

\section{SERVICE \& PROFESSIONAL ACTIVITIES}
\begin{itemize}
\item UNL ACM President -- 2007-2009
\item Attended International Summer School on Grid Computing in Nice, France.  Summer 2009
\item Student Volunteer at SuperComputing.  November 2009
\item Research Internship at Fermi National Accelerator Laboratory in Chicago, IL.  Summer 2010 
 \item Assisted teaching at the OSG Summer School.  July 2010
 \item Organized and Ran the OSG Intro Campus Grids Meeting.  October 2010
 \item Displayed my real-time visualizations at the UNL/FNAL SuperComputing Booth, New Orleans.  November 2010
\item Attended CMS Week at CERN, Geneva, Switzerland.  April 2011
\end{itemize}




             
  
          
\end{resume}



%\bibliographystyle{alpha}
%\bibliography{DerekWeitzelResume.bib}
\end{document}




